---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# poispalette

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.com/poissonconsulting/poispalette.svg?branch=master)](https://travis-ci.com/poissonconsulting/poispalette)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/poissonconsulting/poispalette?branch=master&svg=true)](https://ci.appveyor.com/project/poissonconsulting/poispalette)
[![Codecov test coverage](https://codecov.io/gh/poissonconsulting/poispalette/branch/master/graph/badge.svg)](https://codecov.io/gh/poissonconsulting/poispalette?branch=master)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/licenses/MIT)
<!-- badges: end -->

## Introduction

`poispalette` is an R package that facilitates the use of Poisson Consulting colour palettes in data plots and maps.


## Installation

To install the latest development version from [GitHub](https://github.com/poissonconsulting/poispalette)
```r
# install.packages("remotes")
remotes::install_github("poissonconsulting/poispalette")
```

To install the latest developmental release from the Poisson drat [repository](https://github.com/poissonconsulting/drat)
```r
# install.packages("drat")
drat::addRepo("poissonconsulting")
install.packages("poispalette")
```

## Demonstration
```{r example}
library(ggplot2)
library(poispalette)

ggplot(poispalette::points, aes(x = RandomX, y = RandomY)) +
  geom_point(aes(colour = ID), size = 2) +
  poispalette::scale_colour_disc_pois()

ggplot(poispalette::points, aes(x = X)) +
  geom_histogram(aes(fill = ID), binwidth = 30) +
  poispalette::scale_fill_disc_pois()

ggplot(poispalette::lines, aes(x = DateTimeData, y = Value)) +
  geom_line(aes(colour = ID), size = 2) +
  poispalette::scale_colour_disc_pois(palette = "legacy")
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/poispalette/issues).

[Pull requests](https://github.com/poissonconsulting/poispalette/pulls) are always welcome.

Please note that this project is released with a [Contributor Code of Conduct](https://github.com/poissonconsulting/poispalette/blob/master/CODE_OF_CONDUCT.md).
By contributing, you agree to abide by its terms.
