---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# poispalette 

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/poissonconsulting/poispalette/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/poissonconsulting/poispalette/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/poissonconsulting/poispalette/branch/master/graph/badge.svg)](https://codecov.io/gh/poissonconsulting/poispalette?branch=master)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/licenses/MIT)
<!-- badges: end -->

## Introduction

`poispalette` is an R package that facilitates the use of Poisson Consulting colour palettes in data plots and maps.


## Installation

To install the latest development version from [GitHub](https://github.com/poissonconsulting/poispalette)
```r
# install.packages("remotes")
remotes::install_github("poissonconsulting/poispalette")
```

## Demonstration

Retrieve Poisson colours and palettes
```{r}
library(poispalette)

pois_pal("discrete")

pois_cols(c("red", "yellow"))

```

Plot discrete scales
```{r}
library(ggplot2)

ggplot2::ggplot(poispalette::points, aes(x = RandomX, y = RandomY)) +
  geom_point(aes(colour = ID), size = 2) +
  scale_colour_disc_poisson()
```

Plot gradient scales
```{r}
ggplot2::ggplot(poispalette::points, aes(x = X, y = Y)) +
  geom_point(aes(colour = RandomX), size = 2) +
  scale_colour_grad_poisson(palette = "cool")

```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/poispalette/issues).

[Pull requests](https://github.com/poissonconsulting/poispalette/pulls) are always welcome.

## Code of Conduct

Please note that the poispalette project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
